Data cleaning and processing script

### 2023-03-02 code/processing_code/data_processing_LML.qmd
exploratory analysis

>>>>

### Calculate percent positive of technical reps

```{r}
wbe_tr <- wbe_year2 %>% group_by(date, facility, target, biological_replicate) %>% 
  dplyr::summarise(
    n=n(), 
    n.miss=sum(is.na(ct)), 
    ct.mean=mean(ct,na.rm=T), 
    ct.sd=sd(ct,na.rm=T)
  ) %>% 
  mutate_all(function(x){ifelse(is.nan(x), NA, x)}) %>% 
  ungroup() %>% 
  mutate(n.pos = n - n.miss) %>% 
  mutate(pos = ifelse(n.pos > 0, "pos", "neg"))
wbe_tr
saveRDS(wbe_tr,here("data/processed_data/wbe_technical_reps.rds"))
```

### Calculate percent positive per biological replicate

```{r}
wbe_br <- wbe_tr %>%
  group_by(date, facility, target) %>% 
  dplyr::summarise(
    n.bio = n(),
    n.bio.non.miss = sum(!is.na(ct.mean)),
    n.bio.miss = sum(is.na(ct.mean)),
    n.total = sum(n), 
    n.total.miss = sum(n.miss), 
    bio.ct.mean = mean(ct.mean, na.rm = T), 
    bio.ct.sd = sd(ct.mean, na.rm=T), 
    tech.ct.dists = paste(paste0(biological_replicate, " = ", round(ct.mean,2), " (sd=", round(ct.sd,2), ", n=", n-n.miss, ")"), collapse = "; ")
  ) %>%
  mutate_all(function(x){ifelse(is.nan(x), NA, x)}) %>% 
  ungroup()
wbe_br
```

### Calculate percent positive per sample

```{r}
wbe_samp <- wbe_br %>%
  group_by(date, facility, target) %>% 
  dplyr::summarise(
    n.pos = sum(!is.na(bio.ct.mean)),
    n.miss = sum(is.na(bio.ct.mean))) %>%
  mutate_all(function(x){ifelse(is.nan(x), NA, x)}) %>% 
  ungroup() %>% 
  mutate(prop.pos = n.pos/(n.pos+n.miss)*100)
wbe_samp
```

```{r}
ggstatsplot::ggbarstats(
  data = wbe_samp,
  x = n.pos,
  y = target) +
  labs(caption = NULL)
```
